%\let\nofiles\relax % important for lastpage package to compile
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A,LAE,T1]{fontenc}
\usepackage[arabic,USenglish]{babel}
\usepackage[top=.44in, bottom=.81in, left=.81in, right=.81in]{geometry}
\usepackage[colorlinks,urlcolor=black,linkcolor=black,pdfstartview=FitH,bookmarks=false,urlcolor=blue]{hyperref}
\usepackage{enumitem}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{pacioli}
\usepackage{xcolor}
% allow footer...
\pagestyle{fancy}
%%

\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Faris B. Mismar\hfill \href{mailto:faris.mismar@ieee.org}{\nolinkurl{faris.mismar@ieee.org}} \hfill Page \thepage\ of 3}%\pageref{LastPage}} % some times you will get ?? for page number. recompile the .tex file and hopefully it will become a number

\begin{document}
\title{Faris Mismar's Resume}
\section*{\centering\LARGE \textsc\textbf{Faris B. Mismar}}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
(214) 912-3263  & \href{https://www.linkedin.com/in/farismismar}{\nolinkurl{https://www.linkedin.com/in/farismismar}} \\
Plano, TX 75025 & \href{mailto:faris.mismar@ieee.org}{\nolinkurl{faris.mismar@ieee.org}} \\
\end{tabular*}
\hrule
\vspace{-0.1in}
%\section*{\centering \large \textsc{Sr. Manager, Software Engineering}}
%\section*{\centering \large \textsc{Consultant, Business Development}}
%\section*{\centering \large \textsc{Director, Radio Access Quality Assurance}}
%\section*{\centering \large \textsc{VP Chief Technology Officer \& Strategy}}
%\section*{\centering \large \textsc{Principal Data Scientist and Radio Access Expert}}
\section*{\centering \large \textsc{Director, 5G NR Wireless, Machine Learning/Artificial Intelligence}}
An accomplished leader with 15+ years of experience in wireless communications including leading others and 2+ years of experience in machine learning in creating and selling products and services. Excellent project leadership and communication skills.  Proven track of interfacing and consulting with executives.

% You must change these to reflect the job you are applying to.
\begin{center}
\textbf{Core Competencies:} Consultative Sales $\blacksquare$ Project Leadership $\blacksquare$ Innovation $\blacksquare$ Presentation Skills $\blacksquare$ Conflict Management $\blacksquare$ Problem Solving $\blacksquare$ Machine Learning $\blacksquare$ Software Development $\blacksquare$ 3gpp RAN Standards
\end{center}

%\vspace*{-0.2in}
\subsection*{\sc \centering Professional Experience}
\textbf{Reliance Jio Infocomm Limited, Frisco, TX\hfill 2018-Present}\\
%\textbf{Sr. Manager, Product and Technology Development\hfill \normalfont 2018-Present}
\textbf{Director, Product and Technology Development\hfill \normalfont 2018-Present}
\begin{itemize}
\item I report to the VP of Technology Development. I am helping disrupt our 5G NR development paths forward with focus on Massive MIMO and Mobile Edge Computing (MEC) products development. I am also working on employing advanced machine learning techniques in the radio network.
\end{itemize}
\textbf{ERICSSON, Plano, TX\hfill 2009-2018}\\
\textbf{Solutions Manager II -- RAN and Machine Learning \hfill\normalfont 2015-2018}
\begin{itemize}
\item Served as machine learning authority role at Ericsson, Business Area Digital Transformation. 
\item Provided sales support for customers both in North America and around the globe. Examples of involved verticals: energy controllers, transport and logistics, and telcos (products and services).
\item Developed algorithms using machine learning (supervised and unsupervised) to create actionable insights for several high visibility customer use cases. Use cases spanned traditional telecommunication cases, end-user experience, and IoT. 
\item Designed and built an engine for predictive data analytics using machine learning for several operators and enterprise customers using Python 3 on highly scalable environments.%  (including scikit-learn, Keras (with both Theano and TensorFlow backends), and other packages), SAS, MATLAB, R, Alteryx, and KNIME.  (e.g., Pentaho connecting to Hadoop (HBase and Impala) and Azure). 
\item Familiar with Agile principles and software development lifecycle.
\item Delivered presentations in several Ericsson workshops held globally for machine learning (algorithms, platforms, and XaaS). 
\item Key contributor to the Ericsson v Apple global patent litigation (UMTS and LTE radio access standards). Press release on Dec 21, 2015 has settlement details.
\item Last day of work: November 10, 2017.  Last day on payroll: Februrary 8, 2018.
\end{itemize}
\textbf{Solutions Manager II -- RAN\hfill\normalfont 2013-2015}
\begin{itemize}
\item Interfaced with CTOs and CTO teams from several customers and CUs on NDO topics. 
\item Functioned as technology authority for new technology introductions: eMBMS (NPO in Netherlands) and 5G NR testbed (AT\&T). 
\item Chaired the Outdoor Heterogeneous Networks Experts Forum global initiative (15 members). 
\item Performed Customer Solutions role in a very high visibility LTE KPI RFP response acceptance, and contract negotiation (NDO) in Indonesia (XL Axiata) to improve Ericsson's O2C process efficiency without compromising on the LTE network quality. 
\item Authored an internal process document which helped win and deliver the service of identifying businesses closest to strands for a leading multi-system operator (MSO) as part of their public Wi-Fi hotspot deployment plan. 
\item Operated as a Consultant for the solution on Heterogeneous Networks strategic planning and design (NDO) to C-suite customers in Australia (VHA) and Saudi Arabia (Mobily). 
\item Performed SON-OM KPI analysis and reporting to Verizon for a 10 MHz LTE cluster on 700 MHz and AWS bands. 
\item Generated sales leads and performed sales support (costing and pricing and presentations). 
\item Engaged as a speaker in several global knowledge sharing events (Centra sessions). 
\item Delivered training for in-building solutions design using iBwave and capacity dimensioning for HSPA+ and LTE in many countries: USA, Spain, Australia, and India. 
\item Spoke in several workshops held globally for heterogeneous networks (products, services, and pre-sales). 
\end{itemize}
\textbf{Solutions Architect III -- RAN\hfill\normalfont 2011-2013}
\begin{itemize}
\item Certified senior member of Competence Domain RAN, Network Design and Optimization (NDO) Global Competence Hub, Global Services. 
\item Executed Customer Solutions Responsible (CSR) role for one small-track project with SaskTel Canada. 
\item Consulted with operators on LTE spectrum bidding (700 MHz vs 2600 MHz). 
\item Identified and qualified sales opportunities. 
\item Performed RF capacity planning and forecast for LTE (including VoLTE), HSPA+, and Wi-Fi. 
\item Developed small cells strategy and planning for AT\&T. 
\item Conducted technical pre-sales customer engagements with AT\&T and other accounts. 
\item Led global teams of varying seniority levels, backgrounds, geographical locations, and cultures. 
\item Authored technical guidelines and white papers on small cells, connected devices, and smartphones. 
\item Tuned and optimized an LTE cluster (10 MHz; 700 MHz and 2100 MHz) in AT\&T. 
\item Participated as a speaker in global and regional knowledge sharing events. 
\item Subject Matter Expert and Business Builder for Ericsson in Mobile World Congress 2013.
\end{itemize}
\textbf{RF Services Engineer IV\hfill\normalfont 2009-2011}
\begin{itemize}
\item Facilitated the Stay Green initiative as the Regional Lead.
\item Interfaced with AT\&T executives and market managers on special events. 
\item Led the RF design for the Dallas Cowboys Stadium for AT\&T HSPA+ radio coverage.
\item Collaborated with AT\&T Labs on WCDMA RF capacity modeling.
\item Led a team to help improve an internal trace analysis tool.
\item Led pre-sales effort for high-profile projects.
\end{itemize}
\textbf{Free Lancing Consultant \hfill 2008-2009} \\
\textit{At Ericsson:}
\begin{itemize}
\item South East regional lead for the Go to Green NPI initiative.  I worked on improving AT\&T CQI KPI metrics on retainability, accessibility, IRAT, ISDR, and 3G on 2G. (Hired through Networkers International MSB).
\end{itemize}
\textit{At AT\&T:}
\begin{itemize}
\item Assisted the AT\&T market team in Seattle, WA in answering to the regional and national teams.
\item Implemented engineering designs to double the cellular capacity of the network as a result of the iPhone 3G launch. (Hired through LCC International Inc).
\end{itemize}
\newpage\noindent
\textbf{MOTOROLA, Middle East (Jordan, Kuwait, Saudi Arabia)\hfill 2004-2008}\\
\textbf{RAN Professional Services Manager\hfill\normalfont 2007-2008}
\begin{itemize}
\item Managed a team of four engineers.
\item Key contributor to the 3G network planning and rollout for Zain in Saudi Arabia.
\item Achieved improved data-centric KPIs through RF optimization for Zain in Kuwait.
\item Handled end-to-end investigation for deteriorated circuit and packet switching user experience. 
\item Implemented 3G/HSPA VIP call trace analysis and recommended features and parameter changes.
\item Drove the effort to improve the most vital and important coverage areas. 
\end{itemize}
\textbf{UTRAN Services Team Leader\hfill\normalfont 2006-2007}
\begin{itemize}
\item Led the operations for all the RNC5000 (Huawei RAN BSC6810) at Zain Kuwait with minimal 3PV support (configuration, feature introduction, and HW/SW upgrades).
\item Designed and implemented Iub, Iur, and Iu interfaces (IP and ATM). 
\item Planned and executed O\&M IP network planning and the corresponding VLAN tagging. 
\item Engineered QoS parameters for IP Iub and Dual Stack Iub. 
\item Configured and administered OMC-U running on Solaris.
\end{itemize}
\textbf{Systems Engineer\hfill\normalfont 2004-2005}
\begin{itemize}
\item Structured and tested softswitching, VoIP media gateways, and HSS for roaming in Jordan (Fastlink). 
\item Performed UNIX administration and shell scripting. 
\end{itemize}
\begin{center}
\subsection*{\sc Education}
\textbf{The University of Texas at Austin, Austin, Texas, USA} \\
Ph.D. in Electrical and Computer Engineering (DICE), Machine Learning and Wireless Networks, December 2020 (expected).  Supervisor: Prof. Brian L. Evans. \\
\vspace*{0.1in}
\textbf{The University of Texas at Dallas, Richardson, Texas, USA} \\
Professional MBA, Organizations, Strategy, and International Management, GPA: 4.000 out of 4.000. \textit{Graduated with High Distinction}.\\
\vspace*{0.1in}
\textbf{The University of Texas at Dallas, Richardson, Texas, USA} \\
Master of Science in Electrical Engineering, Concentration in Communications, GPA: 4.000 out of 4.000. \\
\vspace*{0.1in}
\textbf{The University of Jordan, Amman, Jordan} \\
BSc. in Computer Engineering, GPA: 3.78 out of 4.00.  Ranked number 1 in class.
\end{center}
\newpage
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Faris B. Mismar\hfill \href{mailto:faris.mismar@ieee.org}{\nolinkurl{faris.mismar@ieee.org}} \hfill (\thepage)} % some times you will get ?? for page number. recompile the .tex file and hopefully it will become a number
\pagenumbering{roman}
\setcounter{page}{1}
\section*{\centering \sc \textbf{Addendum}}
\subsection*{\sc Soft-skills Trainings}
Project Leadership, Management, and Communication $\bullet$
Finance for Non-Finance Managers $\bullet$ Presentation Skills $\bullet$ Negotiation Skills and Conflict Management $\bullet$ Project Steering $\bullet$ Leadership Core Curriculum for Individual Contributors $\bullet$ Consultation Core Curriculum $\bullet$ SPIN 2.0 $\bullet$ Toastmasters International Competent Leader and Competent Communicator $\bullet$ Onboarding for Sales $\bullet$ PMP {\textregistered} \textit{(currently preparing for the exam)}.
\vspace*{-0.1in}
\subsection*{\sc Languages}
English (Fluent), Arabic (Native), Spanish (Intermediate).
\vspace*{-0.1in}
\subsection*{\sc Platforms and Computer Languages}
VMWare, Mac OS X (Darwin), iOS, Solaris, Microsoft Windows, C, C++, MATLAB, Python, R
\vspace*{-0.1in}
\subsection*{\sc Scripting Languages}
PERL, Python, BASH Shell, Windows Command Shell, Javascript
\vspace*{-0.1in}
\subsection*{\sc Honors and Scholarships}
Senior IEEE member since August 2017 $\bullet$ Marcus Wallenberg Foundation Scholarship for Scientific Research and Education, 2016, 2017 $\bullet$ UT Dallas Dean's Excellence Scholarship for Continuing Graduate Students Award, 2013-2014 $\bullet$ Toastmasters International Competent Communicator, November 2013 $\bullet$ Toastmasters International Competent Leader, July 2013 $\bullet$ Ericsson Key Contributor Award presented by Ericsson's former CEO Hans Vestberg, 2013 $\bullet$ UT Dallas SOM Dean's Excellence Scholarship Award, 2012-2013 $\bullet$ Motorola BRAVO! Awards for Q1 2007, Q4 2007, and Q3 2008 $\bullet$ The University of Jordan: Board of Trustees Award for Academic Excellence, 2004.
\subsection*{\sc Patents and Peer-Reviewed Articles}
\begin{itemize}[leftmargin=*]
\item F. B. Mismar and S. Nammi, ``METHODS FOR ADAPTING A REPORTING PERIOD FOR A USER EQUIPMENT,'' U.S. Patent: 9,883,528, issued September 2016.
\item S. Nammi and F. B. Mismar, ``A METHOD TO TRANSMIT SIGNALING RADIO BEARER MESSAGES IN MULTI ANTENNA WIRELESS  SYSTEMS,'' U.S. Patent: US 9,762,456, issued September 2016.
\item F. B. Mismar and B. L. Evans, ``Partially Blind Handovers for mmWave New Radio Aided by Sub-6 GHz LTE Signaling,'' \textit{IEEE International Conference on Communications} \href{https://arxiv.org/pdf/1707.01879.pdf}{\nolinkurl{arXiv:1710.01879}}, May 2018.
\item F. B. Mismar and B. L. Evans, ``Deep Q-Learning for Self-Organizing Networks Fault Management and Radio Performance Improvement,'' \textit{submitted}, \href{https://arxiv.org/pdf/arXiv:1707.02329.pdf}{\nolinkurl{arXiv:1707.02329}}, March 2018.
\item F. B. Mismar and B. L. Evans, ``Q-Learning Algorithm for VoLTE Closed-Loop Power Control in Indoor Small Cells,'' \textit{submitted,} \href{https://arxiv.org/pdf/1707.03269.pdf}{\nolinkurl{arXiv:1710.03269}}, February 2018.
\item F. B. Mismar and B. L. Evans, ``Machine Learning Approach for Improved Downlink Coordinated Multipoint in Heterogeneous Networks,'' \textit{submitted,} \href{https://arxiv.org/pdf/1608.08306.pdf}{\nolinkurl{arXiv:1608.08306}}, August 2016.
%\item F. B. Mismar and B. L. Evans, ``Deep Reinforcement Learning for Improving Downlink mmWave Communication Performance," \textit{IEEE Journal on Selected Topics in Signal Processing, submitted,} 
%\href{https://arxiv.org/pdf/1707.02329.pdf}{\nolinkurl{arXiv:1707.02329}}, June 2017.
\item I. Da Silva, Y. Wang, F. B. Mismar, and W. Su, ``Event-based Performance Monitoring for Inter-System Cell Reselection: A SON Enabler,'' \textit{International Symposium on Wireless Communication Systems}, Paris, Aug 2012.
\end{itemize}
\vspace*{-0.1in}
\subsection*{\sc Volunteering Experience}
\begin{itemize}[leftmargin=*]
\item[-] Classical Arabic linguist and editor-in-chief for K-12 curriculum (\textit{al-Jadeed} Arabic Language Series  \foreignlanguage{arabic}{\textRL{الجَديدُ في اللُّغَةِ العَرَبِيَّةِ}}): a series of textbooks for non-native Arabic language speakers in the USA.  I am currently working on grades 1 through 5.  My contributions are: content (poetry for children), proofreading, grammatical checking, and editorial changes.
\item[-]Google Translate: Level 22 Contributor in English-Arabic translation.  Level 22 Contributor in Arabic-English translation.  Level 2 Contributor in Spanish-Arabic translations (Google stopped this branch for contributions).
\item[-] Wikipedia: I have contributed to contents related to cellular communication, radio access protocols, and mathematics. In Classical Arabic, my contributions are mostly proofreading and editing to ensure that the content continues to preserve the endangered language.
\end{itemize}
\end{document}
